\documentclass[margin,line]{res}
\usepackage[bottom]{footmisc}
\usepackage{comment}
%\topmargin -.7in
	\addtolength{\oddsidemargin}{-.5in}
	\addtolength{\evensidemargin}{-.5in}
	\addtolength{\textwidth}{.9in}

	\addtolength{\topmargin}{-.5in}
	\addtolength{\textheight}{.5in}
%\oddsidemargin -.7in
%\evensidemargin -.7in
%\textwidth=6in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight}

\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{array,booktabs}
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Santiago Pérez Cardona \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{3in}}
Cra 1 \#18A-12             & {\it Personal:} +57 (301) 725-5135 \\            
Department of Economics   & {\it Work:} +57 (601) 339-4949, Ext.2440  \\         
Universidad de los Andes & {\it E-mail:}  \href{mailto:s.perez1@uniandes.edu.co}{s.perez1@uniandes.edu.co}\\       
Bogotá, Colombia  & {\it Web Page:} \href{https://santiago-perezc.github.io}{santiago-perezc.github.io}  \\   
\end{tabular}


\section{\sc Interests}
Development Economics, Labor Economics, Political Economy.

\section{\sc Education}

{\bf Universidad de los Andes}, Bogotá, Colombia\\
{\em Department of Economics} \\
\begin{list1}

\item[]M.A., Economics, \textit{Cum Laude} (Ranked 2\textsuperscript{nd}/14) \hfill  {\it 2020  - 2021}
\item[]$\;\;\;\;\;$Original Scale GPA: 4.82/5; \href{https://applications.wes.org/igpa-calculator/}{WES} iGPA: 4/4 
\item[]
\item[] B.A., Economics (Ranked 6\textsuperscript{th}/123) \hfill {\it 2015 - 2019}
\item[]$\;\;\;\;\;$Original Scale GPA: 4.6/5; \href{https://applications.wes.org/igpa-calculator/}{WES} iGPA: 3.94/4 

\end{list1}

\vspace{.1cm}

\section{\sc Honors and Awards} 

\textit{Cum Laude}, awarded to the top 3\% of the previous 5 years of graduates \hfill  {\it 2022}
\begin{list1}
\item[]Department of Economics, Universidad de los Andes
\end{list1}

Master's Thesis Passed Without Revisions (Grade: 5/5) \hfill  {\it 2022}
\begin{list1}
\item[]Department of Economics, Universidad de los Andes
\end{list1}

Best GPA Award (Awarded to the higher undergraduate GPA in Economics)  \hfill  {\it 2017}
\begin{list1}
\item[]Department of Economics, Universidad de los Andes
\end{list1}

Best GPA Award (Awarded to the higher undergraduate GPA in Government) \hfill  {\it 2017}
\begin{list1}
\item[]School of Government, Universidad de los Andes
\end{list1}

\vspace{.1cm}

\section{\sc Academic Experience}
{\bf Harris School of Public Policy}, The University of Chicago, Chicago, IL

\vspace{-.2cm}
{Pre-doctoral Research Assistant - PI: Prof. \href{https://sites.google.com/site/lrmartineza}{Luis Martínez}  \hfill \emph{2020-01 - present}} \\
{\em \footnotesize - ``Fiscal Rules, Austerity in Public Administration, and Political Accountability: Evidence from a Natural Experiment in Colombia''  %
	with  Prof. \href{https://www.mariacarreri.com/}{Carreri} [\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3929550}{Link}]} 
\vspace{.15cm} \\
{\em \footnotesize  - ``How Resilient Are Exporting Firms? Evidence From Chavez's Trade War With Colombia'' 
	with Prof. \href{https://sites.google.com/site/nicoderoux/}{de Roux} \& \href{https://sites.google.com/view/jorgetovar/home}{Tovar}} 	
\vspace{.15cm} \\
{\em \footnotesize  - ``Displacing the Political Fiscal Cycle: Blessing or Curse?'' 
	with Prof. \href{https://sites.google.com/view/nruiz}{Ruiz}} 	
\vspace{.15cm} \\	
{\em \footnotesize  - ``Dictatorship, Higher Education and Social Mobility'' 
	with Prof. \href{https://harris.uchicago.edu/directory/maria-angelica-bautista}{Bautista}, %
			\href{https://fagonza4.github.io/}{González}, %
			\href{https://sites.google.com/view/pablomh}{Muñoz}, \& %
			\href{https://sites.google.com/site/fcomunozma}{Prem} [\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3597798}{Link}]}

\vspace{-.2cm}
	
{\bf Department of Economics}, Universidad de los Andes, Bogotá, Colombia

\vspace{-.2cm}
{Pre-doctoral Research Assistant - PI: Prof. \href{https://sites.google.com/view/raquelbernal}{Raquel Bernal}} \hfill \emph{2021-05 - present} \\
{\em \footnotesize - ``Early Stimulation and Nutrition: The Impacts of a Scalable Intervention''  %
	with  Prof. \href{https://economics.yale.edu/people/orazio-attanasio}{Attanasio},  %
	\href{https://research.bangor.ac.uk/portal/en/researchers/helen-henningham(ab5999a9-22af-4394-b4f4-89dff9971ad1).html}{Baker-Henningham}, %
	 \href{https://sites.google.com/yale.edu/costasmeghir/home}{Meghir}, % 
	 Pineda , \& Rubio-Codina % 
	[\href{https://academic.oup.com/jeea/article/20/4/1395/6516938?login=true}{Link}]} 
\vspace{.15cm} \\
{\em \footnotesize - ``Understanding the Short-, Medium- and Long-term Impacts of Early Childhood Interventions Across the Globe''  %
	with  Prof. \href{https://gse.rutgers.edu/faculty/milagros-nores/}{Nores}} 
\vspace{.15cm} \\
{\em \footnotesize - ``Natural Disasters and Elections: Evidence from Colombia''  %
	with  Prof. \href{https://cienciassociales.uniandes.edu.co/ciencia-politica/profesores/angelika-rettberg/}{Rettberg} \& Lacouture} 
\vspace{.15cm} 
	
\vspace{-.4cm}

{Pre-doctoral Research Assistant - PI: Prof. \href{https://sites.google.com/view/jorgetovar/home}{Jorge Tovar}} \hfill \emph{2020-01 - 2021-05} \\
{\em \footnotesize - ``National Transfer Accounts, Time Use and Gender-Colombia''  %
	with  Prof. \href{https://sites.google.com/site/piedadurdinola/}{Urdinola}}  \\
{\em \footnotesize - Various projects on taxes and cigarette smuggling in Colombia} 

\vspace{-.1cm}
{Pre-doctoral Research Assistant - PI: Prof. \href{https://sites.google.com/view/danielmejial}{Daniel Mejía}} \hfill \emph{2019-08 - 2020-08} \\
{\em \footnotesize - Various projects on crime and public policy interventions in Colombia.} 

%\vspace{.25cm}

%{\bf School of Government}, Universidad de los Andes, Bogotá, Colombia

%\vspace{-.3cm}

%{\em Research Assistant - PI: Prof. \href{https://arturoharker.weebly.com/}{A. Harker}} \hfill \emph{October 2018 - July 2019}\\

\vspace{.1cm}

\section{\sc Working \\ Papers}

\textit{Let the Rebels Rule? Evidence on the Economic Effects of Rebel Governance in Colombia}.
\begin{list1}
    \item[] Updated: November 2022; CEDE Working Paper 2022-3. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4020344}{[PDF here]}. 
\end{list1}


\textit{Implementation Quality of an Early Childhood Parenting Program in Colombia and Child \\ Development}.
\begin{list1}
    \item[] With: \href{https://sites.google.com/view/raquelbernal}{Raquel Bernal}, \href{https://research.bangor.ac.uk/portal/en/researchers/helen-henningham(ab5999a9-22af-4394-b4f4-89dff9971ad1).html}{Helen Baker-Henningham}, and Maria Gómez  
    \item[] Updated: August 2022. \emph{Submitted}
\end{list1}


\textit{Smuggling, Taxes, and Cigarettes in Colombia}.
\begin{list1}
    \item[] Updated: June 2022. %Link. 
    \item[] With: \href{https://sites.google.com/view/jorgetovar/home}{Jorge A. Tovar}.
\end{list1}

\section{\sc Work in \\ Progress}

\textit{The Effects of Teacher Job Burnout on Child Development}.
\begin{list1}
    \item[] With: \href{https://sites.google.com/view/raquelbernal}{Raquel Bernal} and \href{https://economics.ucsd.edu/graduate-program/about/grad-profiles/cohort%202021/Ferro-maria.html}{Maria de la Paz Ferro}.  
\end{list1}

\textit{Rebel Governance and Economic Development in Colombia}.
\begin{list1}
    \item[] With: \href{https://sites.google.com/site/juanfvargas/}{Juan Vargas},  \href{http://www.miweintraub.com/}{Michael Weintraub}, and  \href{https://wp.nyu.edu/rafaelch/}{Rafael Ch}.  
\end{list1}

\section{\sc Teaching Experience}

{\bf Department of Economics}, Universidad de los Andes, Bogotá, Colombia \\
{\em Teaching Assistant for:} \\
\vspace{-.3cm}
\begin{itemize}
    \item Advanced Econometrics (Masters) to Prof. \href{https://sites.google.com/view/manuelfernandezsierra}{M. Fernández} \hfill \emph{Spring  \& Fall 2020}
    \item Microeconomics I (Undergraduate) to Prof. \href{https://jguerraforero.wixsite.com/joseaguerra}{J. Guerra} \& \href{https://sites.google.com/view/andresmoya}{A. Moya} \hfill \emph{Spring \& Fall 2020}
    \item Evaluating and Designing Public Policy (Masters) to Prof. \href{http://www.orazioattanasio.org/}{O. Attanasio}  \hfill \emph{Summer 2021}
    \item Evaluating Policy and Social Programs (Masters) to Prof. \href{https://sites.google.com/view/raquelbernal}{R. Bernal}  \hfill \emph{Fall 2021}
    \item Applied Economics Seminar (Undergraduate) to Prof. \href{https://sites.google.com/site/nicoderoux/}{N. de Roux}  \hfill \emph{Spring \& Fall 2022}
\end{itemize}



%\section{\sc Research \\ Grants} 
%\begin{itemize}
%    \item 2020 - Colombian Institute for the Assessment of Education ($\sim$\$3,000 USD): ``\textit{The End} of Civil Conflict and Educational Attainment'', with G.D. Orbegozo.
%\end{itemize}

%\section{\sc Professional Experience}
%{\bf Information and Strategic Studies Office}, Bogota's Department of Security and Justice, Bogotá, Colombia

%\vspace{-.3cm}
%{\em Data Analyst} \hfill \emph{January 2019 - April 2019}\\

\vspace{-.2cm}

\section{\sc Skills  and \\ Standardized Tests}

\textit{Languages}: Spanish (Native), English (Fluent - C1 Level - TOEFL: 105/100).

\vspace{-.2cm}

\textit{Programming and Software}: Stata, {\LaTeX}, \textsc{R}, \textsc{GIS}. 

\vspace{-.2cm}

\textit{GRE}: Quantitative Score: 169/170 (93th percentile), Verbal Score: 155/170 (66th percentile).


\section{\sc Relevant \\ Courses}

\begin{tabular}{p{7cm}p{7cm}}
 Real Analysis and Optimization (5/5) &Advanced Econometrics  (5/5)                      \\ 
 Advanced Microeconomics (4.6/5)  & Advanced Macroeconomics (Pass) \\
 Master's Thesis (5/5)   &      \\ 
\end{tabular}

\section{\sc References}

\begin{tabular}{p{7cm}p{7cm}}
   \href{https://sites.google.com/view/raquelbernal}{\textbf{Raquel Bernal}}                           & \href{https://sites.google.com/site/lrmartineza}{\textbf{Luis R. Martínez}}      \\
   Full Professor \& University President                & Assistant Professor            \\     
   Department of Economics                          & Harris School of Public Policy \\   
   Universidad de los Andes                         & The University of Chicago      \\
   Bogotá, Colombia                                 & Chicago, IL, USA               \\   
   \href{mailto:rbernal@uniandes.edu.co}{rbernal@uniandes.edu.co} &    \href{mailto:luismartinez@uchicago.edu}{luismartinez@uchicago.edu} \\
    \addlinespace
   \href{https://www.mariacarreri.com/}{\textbf{Maria Carreri}}                            &  \href{https://sites.google.com/site/nicoderoux/}{\textbf{Nicolás de Roux}}               \\
   Assistant Professor                               &   Assistant Professor                    \\     
   School of Global Policy and Strategy                          &  Department of Economics     \\   
   The University of California San Diego                        &  Universidad de los Andes   \\
   San Diego, CA, USA                                 &   Bogotá, Colombia                       \\      
   \href{mailto:mcarreri@ucsd.edu}{mcarreri@ucsd.edu} & \href{mailto:nicolas.de.roux@uniandes.edu.co}{nicolas.de.roux@uniandes.edu.co}   \\
   \addlinespace
   \href{https://sites.google.com/view/jorgetovar/home}{\textbf{Jorge A. Tovar}}                             &                \\
   Associate Professor                              &                      \\     
   Department of Economics                          &      \\   
   Universidad de los Andes                         &    \\
   Bogotá, Colombia                                 &                      \\      
   \href{mailto:jtovar@uniandes.edu.co}{jtovar@uniandes.edu.co} &  
\end{tabular}

\end{resume}
\end{document}


Assistant Professor, School of Global Policy and Strategy

